Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/introduction.tex
'non-trivial' count

Using the inference-mode of the tool, we applied our tool to our
original corpus (\Cref{sec:evaluation}). Our tool identifies and
infers specifications for roughly 60,000 array computations in the
corpus. Approximately 5,000 of the computations we found are non-trivial,
corresponding to code which is a possible source of errors. This
validates the design of our language in its capability to capture many
core patterns.

>>>>

Using the inference-mode of the tool, we applied our tool to our
original corpus (\Cref{sec:evaluation}). Our tool identifies and
infers specifications for \num{\overallnumStencilSpecs} array computations in the
corpus. Of those computations we found, \num{\overallnonTrivial} are non-trivial,
corresponding to code that we think has a higher potential for errors. This
validates the design of our language in its capability to capture many
core patterns.
